importE2data

### 2018-08-30 E2/analysis/histsWithFitsTwoTarget.Rmd
this is going well
about to remove loss of one-target opposite stream

---
title: "inspect histograms"
author: "Alex Holcombe"
date: "2/26/2018"
output: html_document
---

@@

Fix the variable names if not done

```{r, echo=FALSE, message=FALSE}
#Below should now be done by import
if ('target' %in% names(data)) {
  names(data)[names(data) == 'target'] <-'stream'
  names(data)[names(data) == 'condition'] <-'orientation'
  data$stream[ data$stream==1 ] <- "Left"
  data$stream[ data$stream==2 ] <- "Right"
}
if (is.numeric(data$targetSide)) {
  data$targetSide[ data$targetSide==0 ] <- "Both"
  data$targetSide[ data$targetSide==1 ] <- "Left"
  data$targetSide[ data$targetSide==2 ] <- "Right"
}
if (is.numeric(data$orientation)) {
  #mutate condition to Orientation
  data$orientation[ data$orientation==1 ] <- "Canonical"
  data$orientation[ data$orientation==2 ] <- "Inverted"
}
```

@@

Calc numObservations for each condition
```{r }
#Calc numObservations for each condition. This is needed  for scaling the fine-grained Gaussian
#gaussianScaledforData needs to know.
if (!("nPerCond" %in% colnames(dg))) {
  dfGroups<-  dg  %>%  filter( !is.na(targetSP) ) %>% group_by_at(.vars = condtnVariableNames) %>% summarise(nPerCond = n())
  #add nPerCond back to parameter estimates
  estimates<- merge(estimates,dfGroups)
}
```

@@

```{r }
# #Calc numObservations to each condition. This is needed only for scaling the fine-grained Gaussian
# #Calc the number of observations for each condition, because gaussianScaledforData needs to know.
# dfGroups<- dg %>% group_by_at(.vars = condtnVariableNames) %>% summarise(nPerCond = n())
# #add nPerCond back to parameter estimates
# estimates<- merge(estimates,dfGroups)

@@

dAC<- dplyr::filter(dg,subject=="AC")  
bothSides<- dAC %>% filter(targetSide=="Both")
bothSidesCurves <- curves %>% filter(subject=="AC") %>% filter(targetSide=="Both")

@@

```{r singleTarget}
oneSide<- dg %>% filter(targetSide!="Both")
oneSideCurves <- curves %>% filter(targetSide!="Both")

>>>>

---
title: "Histograms with fits two targets"
author: "Alex Holcombe"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

@@

@@

@@

```{r }
# The fine-grained Gaussian to potentially plot

@@

dAC<- dplyr::filter(dg,subject=="AC")  
bothSides<- dAC %>% filter(targetSide=="both")
bothSidesCurves <- curves %>% filter(subject=="AC") %>% filter(targetSide=="both")

@@

```{r singleTarget}
oneSide<- dg %>% filter(targetSide!="both")
oneSideCurves <- curves %>% filter(targetSide!="both")

### 2018-08-30 E2/analysis/importE2data.Rmd
about to remove loss of one-target opposite stream

```{r set up functions}

#Loads raw data from MATLAB files for second backwards paper second experiment
require(R.matlab)

@@

Break out into target position -3, -2 etc. the targetStreamOrient variable that contains the orientaiton of each item. This will allow seeing whether having several orientations in a row triggers the lateral bias.

```{r veryTimeConsuming}
#Need to decompose into SPE=-3 orientation, SPE=-2 orientation, etc.
#Hm, can I use list apply to go through every row and pull out relevant bits?
#Very time-consuming!
Ee$orientMinus3<- -99; Ee$orientMinus2<- -99; Ee$orientMinus1<- -99; Ee$orient0<- -99; Ee$orientPlus1<- -99; Ee$orientPlus2<- -99;

@@

>>>>

```{r set up functions}
#Loads raw data from MATLAB files for second backwards paper second experiment
require(R.matlab)

@@

Break out into target position -4, -3, -2 etc. the targetStreamOrientation variable that contains the orientation of each item. This will allow seeing whether having several orientations in a row triggers the lateral bias.

```{r veryTimeConsuming}
#Need to decompose into SPE=-3 orientation, SPE=-2 orientation, etc.
#Hm, can I use list apply to go through every row and pull out relevant bits?
#Very time-consuming!
Ee$orientMinus4<- -99; Ee$orientMinus3<- -99; Ee$orientMinus2<- -99; Ee$orientMinus1<- -99; Ee$orient0<- -99; Ee$orientPlus1<- -99; Ee$orientPlus2<- -99;

@@

Sanity check the orientMinus4, orientMinus3, etc.
What I don't understand is why the anti-diagonal (the frequency of orientations on two different frames being different rather than being the same orientation)
Maybe it's related to half of those being the same stream and half the opposite stream?

I've checked some individual streams and they don't have any obvious constraints, look random.

Because allLetterOrientations didn't have second dimension, unlike allLetterOrder, I assumed only the target stream was saved (after all, both have same orientation) and I called it targetStreamOrientations. I have now done code review of the MATLAB file, DualRSVP_randomOrientationWithinStreams.m

```{r }

table(Ee$orientMinus2,Ee$orientPlus1)

```

Yes, nan targetSP are in there, which are when is one-target trial and reporting other stream
```{r}
Ee %>% filter(is.nan(targetSP) )
```
